An Exploratory Data Analysis of 18 Tafasīr From the Early 8th to the Late 14th

### 2016-11-24 tafaseer_group/results/Paper.Rmd
Adding Maryam to list of authors (sooorrryyyyy!!!!)
Changes to script

---
# Hey Gang! This is an RNotebook intended to be used with RStudio an'it be fly stuff!
# ====================================================================================
# For documentation, check out these links:
# - https://www.rstudio.com/wp-content/uploads/2016/03/rmarkdown-cheatsheet-2.0.pdf
# - http://rmarkdown.rstudio.com/r_notebooks.html (a bit more explanatory)
# - http://rmarkdown.rstudio.com/lesson-1.html (RNotebook is a superset of RMarkdown)
# - https://blog.rstudio.org/2016/10/05/r-notebooks/ (some advanced examples)
# - https://rmflight.github.io/posts/2012/10/papersinRmd.html (comment by a scientist-user)

title: An Exploratory Data Analysis of 18 Tafasīr From the Early 8th to the Late 14th
  Century and Across a Wide Geographical Area Using Corpus Linguistical Methods
author: "F. Blunck, S. Bukhari, T. D. Keppen, J. R. Schmid"
output:
  pdf_document:
    toc: yes
  html_notebook:
    toc: yes
  html_document:
    toc: yes

# ====================================================================================
# Title (above) and outline (below) are just a first draft, please burn and rearrange!
---

@@

Yo, extraction was simple like tha':

```{ruby}
#!/usr/bin/env ruby

files = [1, 2, 3]

files.each do |f|
  # This is actual code and is actually run
  # when compiling the document, so I can't
  # write things that'll break it.
  puts "#{f}: f.download_it_from_the_internets"
  puts "#{f}: f.do_cool_stuff_to_it"
  puts "#{f}: f.save_as_csv"
end
```

>>>>

---
title: An Exploratory Data Analysis of 18 Tafasīr From the Early 8th to the Late 14th
  Century and Across a Wide Geographical Area Using Corpus Linguistical Methods
author: "F. Blunck, S. Bukhari, M. Foradi, T. D. Keppen, J. R. Schmid"
output:
  html_document:
    toc: yes
  html_notebook:
    toc: yes
  pdf_document:
    toc: yes
---

@@

Yo, extraction was simple like tha' أخي:

```{R}
print(paste('Hello', 'world', '!'))
```
